\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\noindent%
I would like to express my thanks to my host organization Harmony Enterprise Solution for accepting me doing the internship. And my supervisor Mr. LE Quoc Dat, who gave me an incredible idea for the project. He also advised me, provided invaluable guidance and reviewed my entire project to make it complete. Secondly, I also would like to exhibit my thanks to my supervisor at the University of Science and Technology of Hanoi (USTH), Dr. TRAN Giang Son, for showing me some lackness in my work, which helps me to never stop expanding the work. I really appreciate my friends, all professors and staff at USTH for helping me the past three incredible years. After all, I express my sincere gratitude to my parents for their patience and their love throughout my life. Sincerely thank!
\noindent%
 \newline

\begin{otherlanguage}{vietnamese}

\vspace{3cm}



{\Large\noindent%
Lời cảm ơn \newline}

\noindent%
Trước tiên, tôi xin gửi lời cảm ơn tới Công ty Harmony Enterprise Solution đã cho tôi cơ hội được hoàn thành thực tập tại Công ty. Và tôi xin được gửi lời cảm ơn sâu sắc tới người hướng dẫn trong ba tháng vừa qua, Anh Lê Quốc Đạt, người đã cho tôi những ý tưởng độc đáo cho dự án này. Anh cũng chỉ bảo, cho tôi những lời khuyên quý giá và giúp tôi hoàn thiện dự án. Thứ hai, tôi cũng muốn gửi lời cảm ơn đến Tiến sĩ Trần Giang Sơn, người đã chỉ ra những thiếu sót của tôi để khiến tôi không ngừng phát triển dự án. Tôi cũng biết ơn sâu sắc tới những người bạn, các giảng viên và các anh / chị nhân viên tại USTH, đã giúp đỡ tôi trong suốt ba năm vừa qua. Cuối cùng, tôi muốn bày tỏ lòng biết ơn sâu sắc tới cha mẹ, vì sự nhẫn nại và tình yêu thương họ dành cho tôi cả cuộc đời này. Xin chân thành cảm ơn!

\end{otherlanguage}
\vspace{3cm}